Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-22 ms.tex
Mehrdad's draft is incorporated

While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is significantly greater, typically $\dot M \sim 10^{-8} M_{\odot}$/yr based on observation \memoYF{to Jason: reference?}. The rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase. 
Therefore, we have
%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
\begin{equation}
\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
\label{ss:offset}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

While the solar mass loss rate, $\dot M_{\odot }$, is $\dot M_{\odot } \sim 2\times 10^{-14} M_{\odot}$/yr \memoYF{reference needed?}, the mass loss rate of red giants is typically $\dot M \sim 10^{-8}-10^{-7} M_{\odot}$/yr, ant the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase. 
Therefore, we have
%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
\begin{equation}
\frac{\dot M}{\dot M_{\odot}} \sim 10^6 - 10^9
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Back-reaction of a plasma flowing into a magnetic field}
\label{ss:offset}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$. The particles make a spiral motion inside the magnetic field and partially cancel the initial field. The canceling field $B_c$ can be estimated as follows.

A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
%%%
\begin{equation}
r=\frac{mv}{eB}.
\end{equation}
%%%
This creates a magnetic dipole
%%%
\begin{equation}
\mu = \frac{e}{2\pi r/v} \pi r^2 = \frac{1}{2} e r v.
\end{equation}
%%%
The volume integral of the magnetic field generated by a single dipole $\mu$ is
%%%
\begin{equation}
\int d^3{\boldsymbol r} B = \frac{8\pi}{3} \mu.
\end{equation}
%%%
Hence, for a number density $n$ of these charged particles the canceling field is
%%%
\begin{equation}
B_c = \frac{n(mv^2/2)}{3 B^2/8\pi}= \frac{\rho_K}{3\rho_B},
\end{equation}
%%%
where $\rho_K$ and $\rho_B$ are respectively the kinetic energy density and the magnetic energy density. If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.

For a plasma of protons and electrons in solar wind the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
